\subsection{Story: Admins can login to the website and run a session with a quiz}
\subsubsection{Analysis - breakdown of tasks}
This story was large and whilst it will probably be split into a number of tasks, the first task was some spike work on the way this system would work. One route is with WebSockets, a relatively new technology that allows the server to push data to the page quickly and easily\cite{websockets}. This would be a nice solution as it is relatively future proof and a better alternative to other solutions that involve writing a lot of JavaScript and forcing page changes on the users.
\subsubsection{Design}
WebSockets were introduced into Laravel 5 and have become one of the defacto ways to update the front end in real time. Unlike other web frameworks such as Ruby on Rails the web sockets in Laravel requires some extra set up. In Rails the WebSockets can be run on the main web server that is used to run the site\cite{rails-websockets}. In Laravel however another server has to be set up to run these. Laravel offers several different drivers for running the WebSockets, including a Redis server and a third party application called Pusher\cite{laravel-broadcasting}. Pusher handles most of the work for the developer and requires little set up other than creating a free account\cite{pusher-what-is}.
\subsubsection{Implementation}
Pusher was chosen due to its ease of use and due to its high recommendation rate within the Laravel community. A problem with Pusher is that due to it being a third party service, it is not free indefinitely (also it has a number of users limitation). However, you could host your own Redis server to mitigate this cost. This means that the system had to be designed in a way that the driver for WebSockets could be changed with ease.

After configuring the spike work application to use Pusher, a simple Laravel Event was created to send a message to the Pusher. To test this event a couple of methods were implemented. The first method was to register a route that triggers this event when the page is visited.
 
The other method a custom made artisan command that can trigger the event: php artisan quiz:send {message}. A command is useful for testing the event as it can be used without building a button on the front end to trigger it.

Two online guides were used to help write this section of the system due to WebSockets being a new technology\cite{pusher-guide}\cite{echo-guide}. Though they were used to get the basic concepts working, the final code used within the project is tailored to the system and is therefore different overall.
\subsubsection{Testing}
There was no testing as it was spike work.
\newpage

\subsection{Non-story work}
\subsubsection{Refactor controllers}
A problem was that the Eloquent functions for modifying and reading from the database were within the controllers. In a strict MVC system, this functionality should be inside the models. To fix this, the Eloquent functions were refactored into the respective quiz and question models. This would make it easier for future development if anything ever needed to change within the logic concerning any database interactions.
\subsubsection{Changing the database structure}
The original design was changed, and the quiz\_questions table for linking quizzes and questions together was removed. The original reason for this table was that questions could be reused between quizzes. However, after thinking about the potential for that to happen, and the issues that the structure was causing in the model logic, it was decided that the quiz\_question table was more of a hindrance than a help.

The questions table now has a quiz\_id column that references the quiz to which it belongs to. This change means that the relationships between the two tables are much easier to define in the models, having belongsTo and hasMany functions in both that automatically return the objects they own or which they belong to. Thanks to the previous refactoring of model logic, changing this functionality was straightforward. Deleting rows in the database was also simpler now that there was no quiz\_questions table. 

However, when a quiz was deleted, the question associated with it were not automatically deleted. To fix this, the onDelete cascade option was added to the quiz, that means all objects belonging to the quiz being deleted would also be deleted.
\subsubsection{Frontend setup}
This was the first time that any custom CSS was written and Laravel uses SASS to generate its CSS. To build this SASS into CSS, and also to build any future JavaScript, Laravel Mix was needed to run builds for this code. For this, npm and node had to be installed so that they could run their Webpack build scripts. There were some issues trying to get the build scripts to run, even though it worked on fresh installs of Laravel, but eventually a Github issue was discovered that had some solutions\cite{broken-mix}.
\subsubsection{Dusk and Travis}
The aim was to try and set up Laravel Dusk on Travis. Dusk can use a few different browser drivers for running the tests in, by default this is Chrome but Travis comes preconfigured with PhantomJS which is also supported by Dusk. It should be easy to swap the drivers such that Travis can use PhantomJS. Unfortunately this did not work, and no reason could be found. A project that was supposed to run its Dusk tests on Travis was even copied and that does not work, therefore it had to be concluded it is currently not working.
\newpage
