\chapter{Iterations}
\section{Tools used}
There were a number of tools used throughout development that do not fit under a single iteration. The main three were a Wordpress diary, a Trello board and Git. 

The diary was used to keep track of the major pieces of development done each week and any questions/ issues that needed to be raised during supervisor meetings. This was a simple Wordpress site that was set up several years ago and repurposed for the use in this project.

Trello is a project management tool that allows users to create a "board" for a project that then allows the creation of cards that tasks can be added to\cite{trello}. Feature tracking is a key part of the system as tasks and cards can be marked as complete, Trello suits XP based approaches as cards can be created and edited on the fly for each iteration. For this project, a card was created for each iteration, with a list of stories and tasks to be completed within that iteration. Once a task was completed, it was checked as such giving an easy to read percentage completion for the story.

Git was used extensively during development, primarily for version control but also a form of backup and as an easy way to deploy the system. Version control is very important as it allows tracking changes to the project and if a mistake it made, can be used to undo these mistakes. It also allows branching out bits of functionality, so developing features can be done separate from the rest of the project and once working, merged back in. Github was used as the repository service due to it being free and easy to use\cite{github}.
\section{Iteration 0 16/02 - 22/02}
\input{Chapter3/Iter-0/Iter-0}

\section{Iteration 1 23/02 - 01/03}
\input{Chapter3/Iter-1/Iter-1}

\section{Iteration 2 02/03 - 08/03}
\input{Chapter3/Iter-2/Iter-2}

\section{Iteration 3 09/03 - 15/03}
\input{Chapter3/Iter-3/Iter-3}

\section{Iteration 4 16/03 - 22/03}
\input{Chapter3/Iter-4/Iter-4}

\section{Iteration 5 23/03 - 29/04}
\input{Chapter3/Iter-5/Iter-5}

\section{Iteration 6 30/03 - 05/04}
\input{Chapter3/Iter-6/Iter-6}

\section{Iteration 7 06/04 - 12/04}
\input{Chapter3/Iter-7/Iter-7}

\section{Iteration 8 13/04 - 19/04}
\input{Chapter3/Iter-8/Iter-8}

\section{Iteration 9 20/04 - 26/04}
\input{Chapter3/Iter-9/Iter-9}

\section{Iteration 10 27/04 - 03/05}
\input{Chapter3/Iter-10/Iter-10}